Project Thesis/Report

### 2021-12-22 Gandhi_Project_Report/draft1.tex
Nearly at the end of Section 4

\begin{Definition}
  A driven system $g$ is said to have the Unique Solution Property if for each input $\overline{u}$ there exists exactly one solution. Alternatively we may formulate the USP as follows: $g$ has the Unique Solution Property if there exists a well-defined map $\Psi:{U}\to{X}$ where $\Psi({\overline{u}})$ denotes the unique solution 
\end{Definition}

@@

  Note that $\tilde{g}_v$ maps $(\ldots, u_{-2}, u_{-1})$ to $(\ldots, u_{-2}, u_{-1}, g(v, u_{-1}))$.
  The driven system $g$ can induce an embedding of $\overleftarrow{U}$ in $\overleftarrow{X}$ as follows: 
  If $H$ is also injective (and hence bijective), it becomes the embedding of $\overleftarrow{U}$ in $\overleftarrow{X}$ induced by the driven system $g$ and we refer to $H$ as a \emph{causal embedding}. We formalise this in the following definition.

@@

We have not as of yet treated the UAP, and establish the necessary result here (without proof - left to literature or later) so as not to break up the completeness of theorem

@@

We're not getting quite close to where we want to be and our results carry more and more weight. Recall that $g$ is only being given inputs from the orbits of $T$.

\begin{Theorem}
  Graph 1 is exactly the inverse-limit system $(\hat{U}, \hat{T})$.    
\end{Theorem}

>>>>

\begin{Definition}
  A driven system $g$ is said to have the Unique Solution Property(USP) if for each input $\overline{u}$ there exists exactly one solution. Alternatively we may formulate the USP as follows: $g$ has the Unique Solution Property if there exists a well-defined map $\Psi:{U}\to{X}$ where $\Psi({\overline{u}})$ denotes the unique solution 
\end{Definition}

@@

  Note that $\tilde{g}_v$ maps $(\ldots, u_{-2}, u_{-1})$ to $(\ldots, u_{-2}, u_{-1}, g(v, u_{-1}))$.
  The driven system $g$ can induce an embedding of $\overleftarrow{U}$ in $\overleftarrow{X}$ as follows: 
  If $H$ is also injective (and hence bijective), it becomes the embedding of $\overleftarrow{U}$ in $\overleftarrow{X}$ induced by the driven system $g$ and we refer to $H$ as a \emph{causal embedding}.

  Before formalising this, we make mention of the concept of the \emph{inverse-limit system} of a system $(U,T)$. In broad sweeps, the inverse-limit system of a dynamical system is a self-map on a subset of an infinite-dimensional space \textbf{(expand what exactly this is?)} where each point in the inverse-limit space corresponds to a backward orbit of the map $T$. In literature, the inverse-limit space is denoted by $\hat{U}_T\subset\overleftarrow{U}$. \textbf{cite from supp.koopman}. 
  The map $T$, then, induces a self-map $\hat{T}:\widehat{T}: (\ldots,u_{-2},u_{-1}) \mapsto  (\ldots,u_{-2},u_{-1},T(u_{-1}))$ on $\widehat{U}_T$

@@

We have not as of yet treated the UAP, and establish the necessary result here (without proof - left to literature. Or later) so as not to break up the completeness of theorem

@@

We're now getting quite close to where we want to be and our results carry more and more weight. Recall that $g$ is only being given inputs from the orbits of $T$.

\begin{Definition}
  The inverse-limit space $\widehat{U}_T$, a subspace of $\overleftarrow{U}$, is defined by $$\widehat{U}_T:=\{(\ldots, u_{-2}, u_{-1}):T(u_n)=u_{n+1}\}$$ This space is well-defined since $T:U\to{U}$ is surjective by assumption. \textbf{Expand why}
\end{Definition}

\begin{Theorem}
  Graph \ref{Scomm_h} is exactly the inverse-limit system $(\hat{U}, \hat{T})$.    
\end{Theorem}

Note that $H_2$ maps an entire left-infinite solution sequence from $\Psi$ to an element in $X\times{X}$.

We now have the following (compare with \ref{SCausal_H} above):

\emph{graph here causes issues currently}
\begin{center}
%    \[ 
      \psset{arrows=->, arrowinset=0.25, linewidth=0.6pt, nodesep=3pt, labelsep=2pt, rowsep=0.7cm, colsep = 1.1cm, shortput =tablr}
      \everypsbox{\scriptstyle}
      \begin{psmatrix}
      \widehat{U}_T  && \widehat{U}_T \\
      Y_T && Y_T \\
      %%%
     %  \ncline{1,1}{1,2}^{\widehat{T}} \ncline{1,1}{2,1} <{h}
     %  \ncline{1,2}{2,2} > {H_2}
     %  \ncline{2,1}{2,2}^{G_T}
      \end{psmatrix}
     % \]
    \end{center}

\textbf{Show that $(Y_T, G_T)$ is semi-conjugate to $(\widehat{U}, \widehat{T})$. }

\textbf{Summarising the discussing thus far:}
It is easy to lose onself in the symbols, so we take a moment to review our progress up until this point.

\vspace{-8mm}
\begin{enumerate}
\item We are interested in a dynamical system $(U,T)$ with unknown dynamics for whichever reason.
\item To determine information about this system $(U,T)$, we shift our focus by rather aiming to determining the dynamics of the inverse-limit system $(\widehat{U}, \widehat{T})$ which, given certain assumptions, we can guarantee to be at least semi-conjugate to $(U,T)$.
\item If the driven system $g$ (and $\{u_n\}$ in $U$  is an orbit of $T$), we have that $G_T$ exists. 
\item If, furthermore, $g$ may be shown to have the USP, we showed that $(Y_T, G_T)$ is semi-conjugate to $(\widehat{U}, \widehat{T})$.
\item If $T$ is also (and at this stage this is very much our hope) a homeomorphism, then $(Y_T, G_T)$ topologically conjugate to $(\widehat{U}, \widehat{T})$ in which $(U,T)$ has been embedded!

One can therefore learn the single-delay lag dynamics of the driven system states via $G_T$ with enough data thanks to the USP. This enables us to do at least 2 things: 1) Forecast future values of $x_n$ via iterates of $G_T$ (as $G_T$ can be determined. 2) Forecast future values of $u_n$.

\end{enumerate}
